---
title: "Audit Results"
output: html_document
---

In this document, a descriptive analysis of the results of the environmental audits that were conducted along inferred routes between 6 origin-destination pairs in Hamilton, Ontario are presented.

Load packages:
```{r}
library(readr)
library(tidyverse)
library(dplyr)
library(sf)
library(ggthemes)
```

Load data from audits:
```{r}
audit_results <- read_csv("Audit_Results.csv")
Audit_Results_1A <- read_csv("Audit_Results_1A.csv")
Audit_Results_1B <- read_csv("Audit_Results_1B.csv")
Audit_Results_2A <- read_csv("Audit_Results_2A.csv")
Audit_Results_2B <- read_csv("Audit_Results_2B.csv")
Audit_Results_3A <- read_csv("Audit_Results_3A.csv")
Audit_Results_3B <- read_csv("Audit_Results_3B.csv")
```

# Individual Audit Results

## Route 1A

This route is located in West Hamilton, in the lower city, and has 13 segments.

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_1A) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```


## Route 1B

This route is located on the East Mountain and has a total of 12 segments.

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_1B) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```

## Route 2A

This route is located in downtown Hamilton, in the lower city, and has 27 segments.

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_2A) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```

## Route 2B

This route is located in East Hamilton, in the lower city, and has 31 segments.

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_2B) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```

## Route 3A

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_3A) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```

## Route 3B

This route is located in downtown Hamilton, in the lower city, and has 20 segments.

Predominant buildings/features:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.PredominantBuildings))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.PredominantBuildings))
```

Cycling facilities:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.CyclingFacility))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.CyclingFacility))
```

Location of cycling facility:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.FacilityLocation))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.FacilityLocation))
```

Slope:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Slope))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Slope))
```

Road condition:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.RoadCondition))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.RoadCondition))
```

Number of traffic lanes:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Lanes))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Lanes))
```

Presence of traffic calming devices:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.TrafficCalming))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.TrafficCalming))
```

Intersection control:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Crossing))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Crossing))
```

Street lights:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Lights))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Lights))
```

Street maintenance:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Maintenance))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Maintenance))
```

Cleanliness of the street:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Cleanliness))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Cleanliness))
```

Trees:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Trees))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Trees))
```

Attractiveness for cycling:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Attractiveness))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Attractiveness))
```

Difficulty for cycling:
```{r}
ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = A.Comfortability))

ggplot(data = Audit_Results_3B) + 
  geom_bar(mapping = aes(x = B.Comfortability))
```




